---
title: "p8105_hw6_jz3425"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Load the data.

```{r, message=FALSE}
bwt_df = 
  read_csv("data/birthweight.csv")


# check for missing data
bwt_df[rowSums(is.na(bwt_df)) != 0,]

bwt_df %>% 
  filter(pnumsga != 0)

bwt_df %>% 
  filter(pnumlbw != 0)
```

The result shows that there is no missing data, and all `psumsga` and `pnumlbw` = 0 so we could neglect these two variables.

Clean the data for regression analysis.

```{r}
bwt_df =
  bwt_df %>% 
  select(-pnumsga, -pnumlbw) %>% 
  mutate(
    babysex = recode_factor(babysex, `1` = "male", `2` = "female"),
    frace = recode_factor(frace, `1` = "white", `2` = "black", `3` = "asian", `4` = "puerto_rican", `8` = "other", `9` = "unknown"),
    malform = factor(malform),
    mrace = recode_factor(mrace, `1` = "white", `2` = "black", `3` = "asian", `4` = "puerto_rican", `8` = "other")
  ) %>% 
  relocate(bwt)

#have a look
head(bwt_df)
```

### Marginal distribution

First let's see the marginal distribution of each variable.

```{r}
lm_function = function(x) {
  
  lm(bwt_df$bwt ~ x, data = bwt_df) %>% 
    broom::tidy() 
  
}

marginal = 
  bwt_df %>% 
  select(-bwt) %>% 
  map(lm_function)

#have a look at some of the results
marginal[1:5]
```

...

According to the p-values, some of the variables have strong association with birthweight while others do not. 

First I will choose `bhead`, `blength`, `delwt`, `fincome`, `gaweeks`, `mheight`, `momage`, `ppbmi`, `ppwt`, `smoken` and `wtgain` for further tests.

### Testing for pairwise relationship

Among chosen variables, it seems that some of them may have strong linear associasions. Here are some of apparent ones that I find.

```{r, message=FALSE}
bwt_df %>% 
  lm(blength ~ bhead, data = .) %>% 
  broom::tidy()

bwt_df %>% 
  lm(blength ~ gaweeks, data = .) %>% 
  broom::tidy()
```

I will delete `gaweeks` and `bhead` and keep `blength`.

```{r}
bwt_df %>% 
  lm(delwt ~ mheight, data = .) %>% 
  broom::tidy()

bwt_df %>% 
  lm(delwt ~ ppwt, data = .) %>% 
  broom::tidy()

bwt_df %>% 
  lm(delwt ~ ppbmi, data = .) %>% 
  broom::tidy()

bwt_df %>% 
  lm(delwt ~ wtgain, data = .) %>% 
  broom::tidy()
```

I will delete `mheight`, `ppwt`, `ppbmi`, `wtgain` and keep `delwt`.

So my hypothesis is that a child's birthweight is associated with baby’s length at birth, mother’s weight at delivery, mother’s age at delivery, family monthly income, and average number of cigarettes smoked per day during pregnancy.

### Build the model

```{r}
lm_1 = 
  lm(bwt ~ blength + delwt + fincome + smoken + momage, data = bwt_df)

lm_1 %>% broom::tidy()
```

Show a plot of model residuals against fitted values:

```{r, message=FALSE, warning=FALSE}
bwt_df %>% 
  add_residuals(lm_1) %>% 
  add_predictions(lm_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(
    title = "Residual plot",
    x = "Predicted value",
    y = "Residual"
  )
```

As expected, the residual values bounce around 0 (the expected value is about 0).

There is an outlier far away. 

```{r}
#check the outlier
bwt_df %>% 
  add_residuals(lm_1) %>% 
  add_predictions(lm_1) %>% 
  filter(resid > 4000)
```

For this baby, the blength 20 is extremely lower than other observations while the bhead is normal. It looks like a mistake, and it should be checked if possible.

## Compare my model to two others

```{r}
cv_df =
  crossv_mc(bwt_df, 100) %>% 
  mutate(
    lm_1 = map(train, ~lm(bwt ~ blength + delwt + fincome + smoken + momage, data = .x)),
    lm_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    lm_3 = map(train, ~lm(
      bwt ~ bhead + blength + babysex + 
          bhead * blength + blength * babysex + bhead * babysex +
          bhead * blength * babysex, 
    data = .x
    ))
  ) %>% 
  mutate(
    rmse_1 = map2_dbl(lm_1, test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(lm_2, test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(lm_3, test, ~rmse(model = .x, data = .y))
  )

cv_df

cv_df %>% 
  select(rmse_1:rmse_3) %>% 
  pivot_longer(
    rmse_1:rmse_3,
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

My model gets pretty much the same rmse as model 2, but much higher than model 3. Maybe this shows that there are interactions between blength, bhead and babysex.

# Problem 2

```{r, warning=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

boot_sample = function(df){
  sample_frac(df, replace = TRUE)
}
```

Bootstrap

```{r}
set.seed(518)

boot_straps =
  data_frame(
    strap_number = 1:50,
    strap_sample = rerun(50, boot_sample(weather_df))
  )

bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results_1 = map(models, broom::glance),
    results_2 = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results_1, results_2) %>% 
  unnest(results_1, results_2) %>% 
  select(strap_number, r.squared, term, estimate) %>% 
  janitor::clean_names()
```

Plot

```{r}
bootstrap_results %>% 
  filter(term == "tmin") %>% 
  ggplot(aes(x = r_squared)) +
  geom_density() +
  labs(
    title = "Distribution of R Squared",
    x = "R Squared",
    y = "Density"
  )
  

b0 =
  bootstrap_results %>% 
  filter(term == "(Intercept)") %>% 
  pull(estimate)

b1 = 
  bootstrap_results %>% 
  filter(term == "tmin") %>% 
  pull(estimate)

tibble(b0, b1) %>% 
  ggplot(aes(x = log(b0 * b1))) +
  geom_density() +
  labs(
    title = "Distribution of log(β0 * β1)",
    x = "log(β0 * β1)",
    y = "Density"
  )
```

Compute CI

```{r}
bootstrap_results %>% 
  filter(term == "tmin") %>% 
  summarize(
    ci_lower = quantile(r_squared, 0.025),
    ci_upper = quantile(r_squared, 0.975)
  )

tibble(b0, b1) %>% 
  summarize(
    ci_lower = quantile(log(b0 * b1), 0.025),
    ci_upper = quantile(log(b0 * b1), 0.975)
  )
```


